<i>invivoPKfit</i> and <i>CvTdb</i> figures

### 2022-11-28 MainAnalysis.Rmd
Updated time stamping in MainAnalysis.Rmd

Set a timestamp: today's date. (I am changing this to YYYYMMDD format -- better sorting by filename. -- CLR)

```{r, set_file_timestamp, eval = TRUE}
THIS.DATE <- "2022_11_21"
```

Run a one-compartment fit on the data, and write out the results.

@@

write.csv(PK.fit.table.1comp, paste("inst/ext/PK_fit_table_1comp_",THIS.DATE,".csv",sep=""), row.names = FALSE)

@@

```{r, run_invivoPKfit_2comp, eval = FALSE}
### do 2-Compartment fit
system.time(PK.fit.table.2comp <- fit_all(
  data.set = cvt.data,
  model = "2compartment",
  modelfun = "analytic",
  compound.col = "analyte_name_original",
  dtxsid.col = "dsstox_substance_id",
  cas.col = "dsstox_casrn",
  reference.col = "fk_reference_document_id",
  species.col = "species",
  species.weight.col = "weight_kg",
  species.weight.units.default = "kg",
  dose.col = "dose_level_normalized",
  time.col = "time_hr",
  time.units.default = "hr",
  media.col = "conc_medium_normalized",
  media.units.default = "normalized",
  value.col = "conc",
    units.default = NA,
  route.col = "administration_route_normalized",
  source.col = "document_id",
  loq.col ="calc_loq",
  subject.default = NA,
  info.default = NA,
  suppress.messages = TRUE
))
write.csv(PK.fit.table.2comp, paste("inst/ext/PK_fit_table_2comp.",THIS.DATE,".csv",sep=""), row.names = FALSE)

>>>>

Run a one-compartment fit on the data, and write out the results. Timestamp the file name with the current date and time in format YYYY_MM_DD_hh_mm_ss.

Fit the 1-compartment model.

@@

write.csv(PK.fit.table.1comp,
          paste("inst/ext/PK_fit_table_1comp_",
                                    format(Sys.time(), "%Y_%m_%d_%H_%M_%S"),
                                    ".csv",
                                    sep=""),
          row.names = FALSE)

@@

Fit the 2-compartment model.

```{r, run_invivoPKfit_2comp, eval = FALSE}
devtools::load_all("invivopkfit")

### do 2-Compartment fit
system.time(PK.fit.table.2comp <- fit_all(
  data.set = cvt.data,
  model = "2compartment",
  modelfun = "analytic",
  compound.col = "analyte_name_original",
  dtxsid.col = "dsstox_substance_id",
  cas.col = "dsstox_casrn",
  reference.col = "fk_reference_document_id",
  species.col = "species",
  species.weight.col = "weight_kg",
  species.weight.units.default = "kg",
  dose.col = "dose_level_normalized",
  time.col = "time_hr",
  time.units.default = "hr",
  media.col = "conc_medium_normalized",
  media.units.default = "normalized",
  value.col = "conc",
    units.default = NA,
  route.col = "administration_route_normalized",
  source.col = "document_id",
  loq.col ="calc_loq",
  subject.default = NA,
  info.default = NA,
  suppress.messages = FALSE
))
write.csv(PK.fit.table.2comp, paste("inst/ext/PK_fit_table_2comp_",
                                    format(Sys.time(), "%Y_%m_%d_%H_%M_%S"),
                                    ".csv",
                                    sep=""), row.names = FALSE)
